Design of Adaptive Constellations and Error Protection Coding for Wireless Network Coding in 5-node Butterfly Networks

### 2017-05-31 response_letter/response_letter.tex

\begin{itemize}
  \item CQ3: \emph{Typos and Formatting Issues}
  \item A3: The manuscript was carefully proofread by native speaker for typos. Regarding the
  formatting issues, we searched and corrected the issues we found. Nevertheless, we should stress
  that the manuscript will be transformed to the EURASIP template prior to publishing and there will
  be time for fine tuning.
\end{itemize}

\begin{itemize}
  \item CQ4: \emph{Motivation beyond the proposed Adaptive Constellation Design and its
  Generalization}
  \item A4: We answer this question in two levels. We split the problem to 1) the wireless
  aware network coding, that is to determine the information flow within the network
  \cite{Uricar-Hynek-Prochazka-Sykora_2013} and 2) the particular constellations 
  design suited for a given information stream. Note that the motivation can be found also in
  \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}.

  The network information flow within the butterfly network can be seen as a combination of the
  cases, when a) all information is passed through the relay b) maximal information is passed
  through the site links as it is explained in \cite{Prochazka_Tutorial_WNC}. Finding a proper
  network information flow within a general wireless network can be a nutshell. Intuitively, the
  wireless network paradigm should be exploited as much as possible due to its higher spectral
  efficiency. To the best of our knowledge, no such approach is available for a general network
  in the current state of the art. The random network coding does not take advantage to be 
  "wireless aware" due to its randomness. There remains a white space for research to bring light
  into a proper network information flow design within a general network.

  The second part of the design assumes a given network information flow and the goal is to find
  the best possible constellation design across the nodes within the network for the given flow.
  Within this design, we consider two building blocks  for multiple access channel, that is: 
  i) orthogonal constellation design forming a non-overlapping superimposed
  constellation in the receiving node enabling joint (full) decoding and ii) hierarchical
  constellation design allowing some overlaps in the received constellation, such that only a
  network function of the data can be recovered (not both individual data streams). Finally, one
  needs to properly combine the aforementioned building blocks by means of superposition coding.

  In case of the orthogonal design, we chosen ASK source constellations mutually shifted by $\pi/2$
  to form the QAM constellation in the received node. This assumes exactly two transmitting nodes.
  For generalization to more sources, some way to preserve join decodability must be found, for
  instance additional resources. The hierarchical design depends on a particular
  network function (exclusive OR in our case). The goal is a received constellation with maximal
  free distance between the \emph{network coded data}, where overlaps within the network function
  are allowed. Actually these overlaps enable to improve the minimal distance compared to the
  orthogonal design. Since both ASK and the proposed hierarchical constellation can be written as
  composition of properly scaled BPSK constellations, the constellations are fully determined by 
  scaling levels\footnote{Determination of those levels can be found in Algorithm 1, line 3 for
  superposed part and lines 6,7 for basic part.} for individual bit streams.

@@

  Nevertheless, the reviewer has a point that it is unfair to claim the performance of the proposed
  $N_b=1$, $N_s=1$ constellation as throughput gain compared to the zero-throughput QPSK, because
  the proposed constellation design uses the site link and it should be rather compared with some
  reference that is able to use the site link as well. For this purpose, the conventional wireless
  network coding with BPSK constellation with nonzero throughput can be considered for instance,
  however to keep the figure readable, we decided not to add another curve into the plot, because 
  the BPSK performs similarly as  $(N_b=2, N_s=0)$ strategy already shown in the figures.
  Therefore the performance gain statement between $N_b=1$, $N_s=1$ and the
  reference QPSK is omitted in Figures 6-9 in the revised manuscript. Check Figure 
  \ref{Fig:Throughput_comparison}) in this response letter to see the change in the figure. 
\end{itemize}

\begin{itemize}
  \item Q: \emph{As far as we know, according to the 3GPP protocol, there is a Channel Quality Index
  (CQI) vs. modulation format table, which suggests the modulation scheme with respect to difference
  SNR range. According to this table, for example, for the SNR varying from 6dB to 20dB, the
  protocol suggests using 16QAM and 64QAM instead of QPSK. In WBN, it could be different from 3GPP,
  but I suggest the author to test some other reference modulation format and compare the
  difference. }
  \item A: The channel quality index is 3-dimensional (MAC, BC and HSI) within our model. Although
  its evaluation can be easily done according to the theoretical analysis, its practical impact is
  questionable, because of more degrees of freedom that comes into
  the consideration in real scenario, like a particular channel code, violation of the idealistic symmetry 
  assumption, strength of the
  direct link, etc. Within our experiment, we manually found some "optimal" table values for a 
  small collection of  SNR tuples in the new section 7.4 (Figures 20, 21), but we would be 
  careful to fix the parameters $(N_b, N_s, r_b, r_s)$ purely according to the SNR triplet in 
  other experiment.
\end{itemize}

\begin{itemize}
  \item Q: \emph{Although, in the future work, the authors have mentioned the fading channel case, it would still be better that the case of fading channels or of longer communication distance could be simulated and experimented. AWGN channel seems to be too ideal. If some initial results on the fading channel case can be added into the paper, it would be better.}
  \item A: We agree that the investigation of the behavior in the fading channels is an important
  step. We have already some initial results available, because we face efficiently to the fading
  channel without the pre-rotation, where the amplitude of the fading coefficients related to the sources
  to relay links is almost (but not completely) equal\footnote{It can be not intuitive that the
  superimposed constellation is determined by relative fading given by the ratio $h=h_A/h_B$ in the 2-step
  setup. The absolute value of fading coefficients can be equally modelled by a corresponding SNR
  value modification.}.   
  A more detailed analysis of the proposed constellation design in fading channels is postponed for further work.
\end{itemize}

### 2017-05-31 Const_design_final.tex
Resubmission

The invention of Wireless Network Coding\emph{ }(WNC) has indeed provided
a means for a significant enhancement in wireless system performance
\cite{Popovski-Yomo_2007a,Nazer-Gastpar_2011-IEEE-P,Zhang-Liew-Lu_2012}.
However, WNC processing has also revealed several non-trivial research
problems which do not have counterparts in conventional point-to-point
or multi-user systems, like the sensitivity to channel parameterization
\cite{Koike-Popovski-Tarokh_2008,Liu-Tao-Xu_2011-ICC,Yasami-Razi-Abedi_2011,Uricar-Sykora_2011}
or challenging multi-source transmission synchronization \cite{Zhang-Liew-Lam_2006b-ITW,Rosetto-Zorzi_2009-SPAWC,Huang-Wang-Song-Guo-Jamalipour_2012-IEEE-T-WC}.
Furthermore, the specific characteristics of multi-node WNC systems
can call also for novel constellation design approaches (see e.g.
\cite{Uricar-Sykora_2011,Prochazka-Uricar-Halls-Sykora_2015-ICC}).

In WNC the transmitted information symbols are allowed to interact
directly in the constellation space, inducing a specific set of requirements
on the constellations' properties and characteristics (see e.g. \cite{Uricar-Sykora_2011,Prochazka-Uricar-Halls-Sykora_2015-ICC}).
Generally we can declare \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}
that any constellation suitable for the specific nature of WNC processing
should be able to form\emph{ a superimposed constellation} with an
appropriate structure at all receiving nodes (allowing direct decoding
of specific WNC functions of user data from the received non-orthogonal
signals \cite{Nazer-Gastpar_2008-ISIT,Sykora-Burr_2011-TVT}) and
simultaneously it should be able to exploit the \emph{broadcast nature
}of wireless channels (allowing a reduction in the consumption of
channel resources in the system \cite{Popovski-Yomo_2007a}). Since
both of these properties hinge on the actual SNR conditions in the
system, the constellation design itself can become a relatively challenging
task.
\begin{figure}
\centering{}
\caption{Symmetric WBN model with half-duplex constraint and 2-phase communication.\label{fig:CTUpp_Information_flows}}
\end{figure}

@@

In this paper we extend the communication scheme from \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}
by appending appropriate \emph{error protection coding} to the system,
resulting in a practical channel-coded adaptive communication scheme
for WBN. We provide the following results and contributions:
\begin{enumerate}
\item We summarize the \emph{systematic constellation design algorithm}
from \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC} and we provide
additional numerical results analysing its promising performance.
\item We revise and extend the results discussing the \emph{adaptive capabilities
of the constellations, }including \emph{the constellation mapping
regions} for adaptive WBN relaying\emph{.}
\item We validate the proposed design in a \emph{real-world HW setup}, including
the HW evaluation of adaptive system performance.
\item We show how the \emph{channel coding} can be integrated into the proposed
constellation design, including the analysis of proper source transmission
rates.
\item We evaluate numerically the performance of the resulting \emph{adaptive
modulation and coding} scheme for a wide range of channel conditions
in the WBN.
\item We show that the proposed design is viable even if the real-world
conditions induce some deviation from the assumed system model.
\end{enumerate}
The rest of the paper is organized as follows. The system model, including
all necessary definitions and details about WNC processing in WBNs
is summarized in Section~\ref{sec:CTUpp_SystemModel}. A systematic
\emph{constellation design algorithm} for WBNs is revised in Section~\ref{sec:CTUpp_Euclidean-Distance-based-Constel}.
The performance analysis of the proposed constellations (including
the HW evaluation) in an uncoded system is available in Section~\ref{sec:CTUpp_Performance-Analysis-Uncoded}.
Section~\ref{sec:CTUpp_Adaptive-Constellation-Design} discusses
an adaptive constellation design and Section~\ref{sec:CTUpp_Channel-Coding}
introduces the channel coding extension to the system. The performance
of the novel adaptive modulation and coding scheme is analyzed in
Section~\ref{sec:CTUpp_Performance-Analysis-Coded}, including a
simple robustness analyzis. Concluding remarks are summarized in Section~\ref{sec:CTUpp_DiscussionConclusions-etc}.

@@

For the sake of simplicity of the theoretical performance analysis,
we assume that source$\rightarrow$relay channels in WBN are AWGN\footnote{Note that this also includes the system with perfect source phase
prerotation \cite{Koike-Popovski-Tarokh_2009a,Zhang-Liew_2010,Anxin-Yuan-Kayama_2008},
which can be obtained by a generalization of the scaling coefficients
as $L'_{n}=L_{n}e^{-\jj\measuredangle h_{SR}}$, where $h_{SR}$ is
the corresponding source$\rightarrow$relay channel.} (i.e. $h_{iR}=1$ for $i\in\{A,B\}$). We evaluate the throughput
analytically as $(N_{b}+N_{s})\cdot(1-P_{e}^{\mathrm{FER}})$, where
$P_{e}^{\mathrm{FER}}$ denotes the frame error rate. Due to the system
symmetry we evaluate the throughput of $S_{A}\to D_{A}$ only. We
set the frame length to $M=768$ symbols (to match the HW evaluation)
and the relay output mapper $\mathcal{A}^{R}$ will be defined as
a conventional ($2^{N_{b}+2N_{s}}$$)$-QAM constellation. All performance
metrics in the symmetric WBN are evaluated as a function of the actual
SNRs ($\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}},\,\gamma_{{\rm {BC}}}$).
\begin{figure*}
\centering{}
\caption{Source constellation design example for $N_{b}=2,\,N_{s}=1$. Resulting
constellations are depicted as blue circles ($S_{A}$ output constellation),
red circles ($S_{B}$ output constellation) and squares (received
superimposed constellation at $R$). Hierarchical function is $f\left(\mathbf{d}_{A}^{b},\,\mathbf{d}_{B}^{b}\right)=\mathbf{d}_{A}^{b}\oplus\mathbf{d}_{B}^{b}$.\label{fig:CTUpp_ConstellationDesignExample} }
\end{figure*}
\begin{figure*}
\begin{centering}
\par\end{centering}

@@

The SNR mapping regions, including the resulting throughput for the
optimal choice of $N_{b}^{{\rm I}},\,N_{s}^{{\rm I}}$, are shown
as a function of $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}}$ for
$\gamma_{{\rm {BC}}}\in\{15\,\mathrm{dB},\,17\,\mathrm{dB},20\,\mathrm{dB},25\,\mathrm{dB}\}$
in Fig.~\ref{fig:CTUpp_SNR_map_BC15-17-20-25}. Several interesting
phenomenas can be again observed in the figure:
\begin{itemize}
\item Since the transmission schemes with ($N_{b}=0,\,N_{s}>0$) constellations
can ignore the HSI channels (Table~\ref{tab:CTUpp_SC-relaying-scheme}),
these constellations are optimal in the low $\gamma_{{\rm {HSI}}}$
region ($\gamma_{{\rm {HSI}}}<8\,\mathrm{dB}$), regardless of the
other channels' SNRs $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}}$.
\item The constellations with ($N_{b}>0,\,N_{s}=0$) provide the best performance
in a substantial part of the medium-to-high $\gamma_{{\rm {HSI}}}$
regions, depending on the actual $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}}$.
\item The \textquotedbl{}combined\textquotedbl{} constellations ($N_{b}>0,\,N_{s}>0$)
provide the maximal throughput (for sufficiently high $\gamma_{{\rm {BC}}}$)
in relatively large regions of $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}}$
(see the dominant throughput regions of $(N_{b}^{{\rm I}},\,N_{s}^{{\rm I}})=(2,1)$
for $\gamma_{{\rm {BC}}}=\left\{ 20\,\mathrm{dB},\,25\,\mathrm{dB}\right\} $).
Note that these constellations have a great potential for application
in systems with limited or partial HSI (see \cite{Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}).
\begin{figure*}
\begin{centering}
\quad
\par\end{centering}

@@

As in the uncoded case, the source nodes $S_{A},\,S_{B}$ in the adaptive
modulation-coding WBN system must be aware of the particular mapping
operation $(\hat{\gamma}_{{\rm {MAC}}},\,\hat{\gamma}_{{\rm {BC}}},\,\hat{\gamma}_{{\rm {HSI}}})\mapsto\left(N_{b}^{\mathrm{II}},\,N_{s}^{\mathrm{II}};\,r_{b}^{\mathrm{II}},\,r_{s}^{\mathrm{II}}\right),$
providing the set of optimal (in the sense of maximal throughput)
constellation/encoder parameters for the given SNR conditions ($\hat{\gamma}_{{\rm {MAC}}},\,\hat{\gamma}_{{\rm {BC}}},\,\hat{\gamma}_{{\rm {HSI}}}$).
Note that, in general, all adaptive system parameters are functions
of the actual SNR conditions in the system. However, we mostly omit
the explicit notation in the following text for to aid readability.

The desired adaptive system parameters can be obtained in the following
two-step procedure. First of all, we analyze the cut-set bound rate
regions $\mathcal{R}^{(N_{b},N_{s})}$ (as discussed in Section \ref{sub:CTUpp_Transmission-Rate-Region})
to identify the maximal encoded system throughput $T_{C}^{(N_{b},N_{s})}$
for a fixed source constellation $(N_{b},N_{s})$:
\begin{align}
T_{C}^{(N_{b},N_{s})}(\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}}) & =\max_{r_{b},r_{s}\in\mathcal{R}^{(N_{b},N_{s})}}(r_{b}+r_{s}),\\
 & =r_{b}^{\mathrm{max}}(N_{b},N_{s})+r_{s}^{\mathrm{max}}(N_{b},N_{s}).\label{eq:CTUpp_opt_rates}
\end{align}
 Then, an exhaustive search over the constellation parameters $N_{b},\,N_{s}$
can be performed to find the maximum encoded system throughput $T_{C}^{\mathrm{max}}$
for the given SNR conditions ($\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}}$):
\begin{equation}
T_{C}^{\mathrm{max}}(\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}})=T_{C}^{(N_{b}^{\mathrm{II}},\,N_{s}^{\mathrm{II}})}=\max_{(N_{b},N_{s})}T_{C}^{(N_{b},N_{s})},\label{eq:CTUpp_Throughput_encoded}
\end{equation}
where $(N_{b}^{\mathrm{II}},\,N_{s}^{\mathrm{II}})$ are the \emph{optimal
source constellation parameters}. The corresponding \emph{optimal
source transmission rates} (\ref{eq:CTUpp_opt_rates}) are given simply
by \emph{$r_{b}^{\mathrm{II}}=r_{b}^{\mathrm{max}}(N_{b}^{\mathrm{II}},\,N_{s}^{\mathrm{II}})$,
$r_{s}^{\mathrm{II}}=r_{s}^{\mathrm{max}}(N_{b}^{\mathrm{II}},\,N_{s}^{\mathrm{II}})$.}
\begin{figure*}
\centering{}
\caption{Maximal encoded system throughput $T_{C}^{\mathrm{max}}$ for $\gamma_{{\rm {BC}}}=7.5\,\mathrm{dB}$
and $\gamma_{{\rm {BC}}}=15\,\mathrm{dB}$.\label{fig:CTUpp_Coded_SNR_map} }
\end{figure*}
\begin{figure*}
\centering{}
\caption{Throughput enhancement $\Delta T_{C}=T_{C}^{\mathrm{max}}-T_{\mathrm{LB}}$
{[}bits/channel use{]} of the coded over uncoded WBN system for $\gamma_{{\rm {BC}}}=7.5\,\mathrm{dB}$
and $\gamma_{{\rm {BC}}}=15\,\mathrm{dB}$. Note that $0.75\leq\Delta T_{C}\leq2$
in the analyzed range of channel SNRs.\label{fig:CTUpp_Coded_ThroughputGain}}
\end{figure*}

@@

\subsection{Robustness Analysis}

In this section we show that the proposed modulation and coding scheme
is viable even if the real world conditions induce some deviations
from the system model assumed in this paper. From a practical point
of view, we would be interested mainly in the situation, where a direct
channel between a source and its desired destination is present (see
Fig.~\ref{fig:CTUpp_DirectChannel}). Even though that this \textquotedbl{}direct\textquotedbl{}
channel can be relatively weak, it inevitably affects the destinations'
HSI observations. In addition to this, we analyse the system where
source phase pre-rotation is switched off (or ineffective due to rapid
channel dynamics), and thus the relay faces a multiple-access channel
with a varying source channel phase offset. This assumption is valid
for a practical system where the applicability of source phase pre-rotation
is limited due to the unavailable ideal feedback channel or because
of the undesirable delay induced by the feedback in the pre-rotation
operation. To demonstrate the robustness of the proposed modulation
and coding strategy, we compare the WBN performance results achieved
by the Monte-Carlo numerical evaluation (see section \ref{sub:Numerical-Simulation-of})
with USRP HW measurements. While in the numerical evaluation we still
keep the idealized assumptions as defined by our system model (i.e.
no direct source$\rightarrow$destination channels, perfect channel
phase pre-rotation), in the HW measurements we now let all data communication
to be performed through real wireless channels (compare with the HW
setup in section~\ref{sub:CTUpp_Hardware_Verification}), introducing
inevitably some direct channel observation at both destinations. In
addition, we allow the source phase pre-rotation to be switched off
in the HW measurements. The channel SNRs $\gamma_{{\rm {MAC}}},\gamma_{{\rm {HSI}}}$
in the HW measurements can be controlled by the source transmit power
adjustment and similarly, particular values of $\gamma_{{\rm {BC}}}$
can be set up by the adjustment of the relay transmit power.
\begin{figure}
\begin{centering}
\par\end{centering}

@@

In this paper we have proposed a systematic algorithm for the design
of two-source constellations in the WBN system. The Algorithm~\ref{alg:CTUpp_ButterflyConstellationDesign}
allows the matching of the constellation parameters to virtually any
SNR conditions in the system, enabling a direct implementation of
the adaptive constellation mapping scheme. The viability of the proposed
constellation design was verified by a means of numerical analysis
and simulations and also by a real-world HW experiment (based on Ettus
Research USRPs), including a HW-based robustness analysis.

@@

In future work, we would like to focus on a full adaptive HW implementation
of the proposed system, where the impact of several other parameters
(e.g. channel fading and dynamics, asymmetry of channel gains etc.)
can significantly affect the system performance and possibly even
require some modifications of the adaptive system design.
\begin{figure*}
\caption{Robustness analysis for two fixed $(N_{b},N_{s},r_{b},r_{s})$ scenarios.
\label{fig:CTUpp_Robustenss_analysis}}
\end{figure*}

>>>>

The invention of Wireless Network Coding\emph{ }(WNC) has provided
a means for a significant enhancement in wireless system performance
\cite{Popovski-Yomo_2007a,Nazer-Gastpar_2011-IEEE-P,Zhang-Liew-Lu_2012}.
However, WNC processing has also revealed several non-trivial research
problems which do not have counterparts in conventional point-to-point
or multi-user systems, like the sensitivity to channel parameterization
\cite{Koike-Popovski-Tarokh_2008,Liu-Tao-Xu_2011-ICC,Yasami-Razi-Abedi_2011,Uricar-Sykora_2011}
or challenging multi-source transmission synchronization \cite{Zhang-Liew-Lam_2006b-ITW,Rosetto-Zorzi_2009-SPAWC,Huang-Wang-Song-Guo-Jamalipour_2012-IEEE-T-WC}.
Furthermore, the specific characteristics of multi-node WNC systems
can call also for novel constellation design approaches (see e.g.
\cite{Uricar-Sykora_2011,Prochazka-Uricar-Halls-Sykora_2015-ICC}).

In WNC the transmitted information symbols are allowed to interact
directly in the constellation space, inducing a specific set of requirements
on the constellations' properties and characteristics (see e.g. \cite{Uricar-Sykora_2011,Prochazka-Uricar-Halls-Sykora_2015-ICC}).
Generally, we can declare \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}
that any constellation suitable for the specific nature of WNC processing
should be able to form\emph{ a superimposed constellation} with an
appropriate structure at all receiving nodes (allowing direct decoding
of specific WNC functions of user data from the received non-orthogonal
signals \cite{Nazer-Gastpar_2008-ISIT,Sykora-Burr_2011-TVT}) and
simultaneously it should be able to exploit the \emph{broadcast nature
}of wireless channels (allowing a reduction in the consumption of
channel resources in the system \cite{Popovski-Yomo_2007a}). Since
both of these properties hinge on the actual SNR conditions in the
system, the constellation design itself can become a relatively challenging
task.
\begin{figure}
\centering{}
\caption{Symmetric WBN model with half-duplex constraint and 2-phase communication.\label{fig:CTUpp_Information_flows}}
\end{figure}

@@

In this paper, we extend the communication scheme from \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}
by appending appropriate \emph{error protection coding} to the system,
resulting in a practical channel-coded adaptive communication scheme
for WBN. We provide the following results and contributions:
\begin{enumerate}
\item We summarize the \emph{systematic constellation design algorithm}
from \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC} and we provide
additional numerical results analysing its promising performance.
\item We revise and extend the results discussing the \emph{adaptive capabilities
of the constellations, }including \emph{the constellation mapping
regions} for adaptive WBN relaying\emph{.}
\item We validate the proposed design in a \emph{real-world hardware (HW) setup}, including
the HW evaluation of adaptive system performance.
\item We show how the \emph{channel coding} can be integrated into the proposed
constellation design, including the analysis of proper source transmission
rates.
\item We evaluate numerically the performance of the resulting \emph{adaptive
modulation and coding} scheme for a wide range of channel conditions
in the WBN.
\item We show that the proposed design is viable even if the real-world
conditions induce some deviation from the assumed system model.
\item We compare the proposed design with state of the art reference scenarios to highlight its
superior performance.
\end{enumerate}
The rest of the paper is organized as follows. The system model, including
all necessary definitions and details about WNC processing in WBNs
is summarized in Section~\ref{sec:CTUpp_SystemModel}. A systematic
\emph{constellation design algorithm} for WBNs is revised in Section~\ref{sec:CTUpp_Euclidean-Distance-based-Constel}.
The performance analysis of the proposed constellations (including
the HW evaluation) in an uncoded system is available in Section~\ref{sec:CTUpp_Performance-Analysis-Uncoded}.
Section~\ref{sec:CTUpp_Adaptive-Constellation-Design} discusses
an adaptive constellation design and Section~\ref{sec:CTUpp_Channel-Coding}
introduces the channel coding extension to the system. The performance
of the novel adaptive modulation and coding scheme is analyzed in
Section~\ref{sec:CTUpp_Performance-Analysis-Coded}, including a
simple robustness analysis. Concluding remarks are presented in Section~\ref{sec:CTUpp_DiscussionConclusions-etc}.

@@

For the sake of simplicity of the theoretical performance analysis,
we assume that source$\rightarrow$relay channels in WBN are AWGN\footnote{Note that this also includes the system with perfect source phase
prerotation \cite{Koike-Popovski-Tarokh_2009a,Zhang-Liew_2010,Anxin-Yuan-Kayama_2008},
which can be obtained by a generalization of the scaling coefficients
as $L'_{n}=L_{n}e^{-\jj\measuredangle h_{SR}}$, where $h_{SR}$ is
the corresponding source$\rightarrow$relay channel.} (i.e. $h_{iR}=1$ for $i\in\{A,B\}$). We evaluate the throughput
analytically as $(N_{b}+N_{s})\cdot(1-P_{e}^{\mathrm{FER}})$, where
$P_{e}^{\mathrm{FER}}$ denotes the frame error rate. Due to the system
symmetry, we evaluate the throughput of $S_{A}\to D_{A}$ only. We
set the frame length to $M=768$ symbols (to match the HW evaluation)
and the relay output mapper $\mathcal{A}^{R}$ will be defined as
a conventional $(2^{N_{b}+2N_{s}})$-QAM constellation. All performance
metrics in the symmetric WBN are evaluated as a function of the actual
SNRs ($\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}},\,\gamma_{{\rm {BC}}}$).
\begin{figure*}
\centering{}
\caption{Source constellation design example for $N_{b}=2,\,N_{s}=1$. Resulting
constellations are depicted as blue circles ($S_{A}$ output constellation),
red circles ($S_{B}$ output constellation) and squares (received
superimposed constellation at $R$). Hierarchical function is $f\left(\mathbf{d}_{A}^{b},\,\mathbf{d}_{B}^{b}\right)=\mathbf{d}_{A}^{b}\oplus\mathbf{d}_{B}^{b}$.\label{fig:CTUpp_ConstellationDesignExample} }
\end{figure*}
\begin{figure*}
\begin{centering}
\par\end{centering}

@@

The SNR mapping regions, including the resulting throughput for the
optimal choice of $N_{b}^{{\rm I}},\,N_{s}^{{\rm I}}$, are shown
as a function of $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}}$ for
$\gamma_{{\rm {BC}}}\in\{15\,\mathrm{dB},\,17\,\mathrm{dB},20\,\mathrm{dB},25\,\mathrm{dB}\}$
in Fig.~\ref{fig:CTUpp_SNR_map_BC15-17-20-25}. Several interesting
phenomena can be again observed in the figure:
\begin{itemize}
\item Since the transmission schemes with ($N_{b}=0,\,N_{s}>0$) constellations
can ignore the HSI channels (Table~\ref{tab:CTUpp_SC-relaying-scheme}),
these constellations are optimal in the low $\gamma_{{\rm {HSI}}}$
region ($\gamma_{{\rm {HSI}}}<8\,\mathrm{dB}$), regardless of the
other channels' SNRs $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}}$.
\item The constellations with ($N_{b}>0,\,N_{s}=0$) provide the best performance
in a substantial part of the medium-to-high $\gamma_{{\rm {HSI}}}$
regions, depending on the actual $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}}$.
\item The \textquotedbl{}combined\textquotedbl{} constellations ($N_{b}>0,\,N_{s}>0$)
provide the maximal throughput (for sufficiently high $\gamma_{{\rm {BC}}}$)
in relatively large regions of $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}}$
(see the dominant throughput regions of $(N_{b}^{{\rm I}},\,N_{s}^{{\rm I}})=(2,1)$
for $\gamma_{{\rm {BC}}}=\left\{ 20\,\mathrm{dB},\,25\,\mathrm{dB}\right\} $).
Note that these constellations have a great potential for application
in systems with limited or partial HSI (see \cite{Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}).
\begin{figure*}
\begin{centering}
\quad
\par\end{centering}

@@

As in the uncoded case, the source nodes $S_{A},\,S_{B}$ in the adaptive
modulation-coding WBN system must be aware of the particular mapping
operation $(\hat{\gamma}_{{\rm {MAC}}},\,\hat{\gamma}_{{\rm {BC}}},\,\hat{\gamma}_{{\rm {HSI}}})\mapsto\left(N_{b}^{\mathrm{II}},\,N_{s}^{\mathrm{II}};\,r_{b}^{\mathrm{II}},\,r_{s}^{\mathrm{II}}\right),$
providing the set of optimal (in the sense of maximal throughput)
constellation/encoder parameters for the given SNR conditions ($\hat{\gamma}_{{\rm {MAC}}},\,\hat{\gamma}_{{\rm {BC}}},\,\hat{\gamma}_{{\rm {HSI}}}$).
Note that, in general, all adaptive system parameters are functions
of the actual SNR conditions in the system. However, we mostly omit
the explicit notation in the following text to aid readability.

The desired adaptive system parameters can be obtained in the following
two-step procedure. First of all, we analyze the cut-set bound rate
regions $\mathcal{R}^{(N_{b},N_{s})}$ (as discussed in Section \ref{sub:CTUpp_Transmission-Rate-Region})
to identify the maximal encoded system throughput $T_{C}^{(N_{b},N_{s})}$
for a fixed source constellation $(N_{b},N_{s})$:
\begin{align}
T_{C}^{(N_{b},N_{s})}(\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}}) & =\max_{r_{b},r_{s}\in\mathcal{R}^{(N_{b},N_{s})}}(r_{b}+r_{s}),\\
 & =r_{b}^{\mathrm{max}}(N_{b},N_{s})+r_{s}^{\mathrm{max}}(N_{b},N_{s}).\label{eq:CTUpp_opt_rates}
\end{align}
 Then, an exhaustive search over the constellation parameters $N_{b},\,N_{s}$
can be performed to find the maximum encoded system throughput $T_{C}^{\mathrm{max}}$
for the given SNR conditions ($\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}}$):
\begin{equation}
T_{C}^{\mathrm{max}}(\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}})=T_{C}^{(N_{b}^{\mathrm{II}},\,N_{s}^{\mathrm{II}})}=\max_{(N_{b},N_{s})}T_{C}^{(N_{b},N_{s})},\label{eq:CTUpp_Throughput_encoded}
\end{equation}
where $(N_{b}^{\mathrm{II}},\,N_{s}^{\mathrm{II}})$ are the \emph{optimal
source constellation parameters}. The corresponding \emph{optimal
source transmission rates} (\ref{eq:CTUpp_opt_rates}) are given simply
by \emph{$r_{b}^{\mathrm{II}}=r_{b}^{\mathrm{max}}(N_{b}^{\mathrm{II}},\,N_{s}^{\mathrm{II}})$,
$r_{s}^{\mathrm{II}}=r_{s}^{\mathrm{max}}(N_{b}^{\mathrm{II}},\,N_{s}^{\mathrm{II}})$.}
\begin{figure*}
\centering{}
\caption{Maximal encoded system throughput $T_{C}^{\mathrm{max}}$ for $\gamma_{{\rm {BC}}}=7.5\,\mathrm{dB}$
and $\gamma_{{\rm {BC}}}=15\,\mathrm{dB}$.\label{fig:CTUpp_Coded_SNR_map} }
\end{figure*}
\begin{figure*}
\centering{}
\caption{Throughput enhancement $\Delta T_{C}=T_{C}^{\mathrm{max}}-T_{\mathrm{LB}}$
[bits/channel use] of the coded over uncoded WBN system for $\gamma_{{\rm {BC}}}=7.5\,\mathrm{dB}$
and $\gamma_{{\rm {BC}}}=15\,\mathrm{dB}$. Note that $0.75\leq\Delta T_{C}\leq2$
in the analyzed range of channel SNRs.\label{fig:CTUpp_Coded_ThroughputGain}}
\end{figure*}

@@

\subsection{Robustness Analysis}\label{sub:Robustness_Analysis}

In this section we show that the proposed modulation and coding scheme
is viable even if the real world conditions induce some deviations
from the system model assumed in this paper. From a practical point
of view, we would be interested mainly in the situation, where a direct
channel between a source and its desired destination is present (see
Fig.~\ref{fig:CTUpp_DirectChannel}). Even though this \textquotedbl{}direct\textquotedbl{}
channel can be relatively weak, it inevitably affects the destinations'
HSI observations. In addition to this, we analyze the system where
source phase pre-rotation is switched off (or ineffective due to rapid
channel dynamics), and thus the relay faces a multiple-access channel
with a varying source channel phase offset. This assumption is valid
for a practical system where the applicability of source phase pre-rotation
is limited due to the unavailable ideal feedback channel or because
of the undesirable delay induced by the feedback in the pre-rotation
operation. To demonstrate the robustness of the proposed modulation
and coding strategy, we compare the WBN performance results achieved
by the Monte-Carlo numerical evaluation (see section \ref{sub:Numerical-Simulation-of})
with USRP HW measurements. While in the numerical evaluation we still
keep the idealized assumptions as defined by our system model (i.e.
no direct source$\rightarrow$destination channels, perfect channel
phase pre-rotation), in the HW measurements we now allow all data communication
to be performed through real wireless channels (compare with the HW
setup in section~\ref{sub:CTUpp_Hardware_Verification}), introducing
inevitably some direct channel observation at both destinations. In
addition, we allow the source phase pre-rotation to be switched off
in the HW measurements. The channel SNRs $\gamma_{{\rm {MAC}}},\gamma_{{\rm {HSI}}}$
in the HW measurements can be controlled by the source transmit power
adjustment and similarly, particular values of $\gamma_{{\rm {BC}}}$
can be set up by the adjustment of the relay transmit power.
\begin{figure}
\begin{centering}
\par\end{centering}

@@

In this paper we have proposed a systematic algorithm for the design
of two-source constellations in the WBN system. The Algorithm~\ref{alg:CTUpp_ButterflyConstellationDesign}
allows the matching of the constellation parameters to virtually any
SNR conditions in the system, enabling a direct implementation of
the adaptive constellation mapping scheme. The viability of the proposed
constellation design was verified by means of numerical analysis,
 simulations and through real-world HW experiments (based on Ettus
Research USRPs), including a HW-based robustness analysis.

@@

In future work, we would like to focus on a full adaptive HW implementation
of the proposed system, where the impact of several other parameters
(e.g. channel fading and dynamics, asymmetry of channel gains etc.)
can significantly affect the system performance and possibly even
require some modifications of the adaptive system design.
